\documentclass[10pt, letterpaper]{article}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{titlesec, enumitem, hyperref, paracol}
\usepackage[dvipsnames]{xcolor}

% Custom formatting
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{1cm}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Mohammad Elayan, MSc}} \\
    PhD Student and Graduate Research/Teaching Assistant \\
    \href{mailto:melayan2@huskers.unl.edu}{melayan2@huskers.unl.edu} | 402-802-6765 \\
    Department of Civil \& Environmental Engineering, University of Nebraska-Lincoln \\
\end{center}

\vspace{0.5cm}

% Profile
\section*{Profile}
I am a PhD student and a Graduate Research Assistant at the University of Nebraska-Lincoln. With over 9 years of experience as a transportation engineering professional in Dubai, UAE, I have contributed to more than 100 projects. My research includes various aspects of transportation engineering, and I have co-authored four publications.

% Education
\section*{Education}
\begin{itemize}[left=0pt]
    \item \textbf{PhD in Civil Engineering – Transportation Engineering} \\
    University of Nebraska-Lincoln, Lincoln, NE, USA \\
    GPA: 4.000 \hfill 2023–Present
    \item \textbf{MSc in Civil Engineering – Transportation Engineering} \\
    Jordan University of Science and Technology, Irbid, Jordan \\
    GPA: 91.6\% (Rank: 1) \hfill 2011–2013
    \item \textbf{BSc in Civil Engineering – Transportation Engineering} \\
    Jordan University of Science and Technology, Irbid, Jordan \\
    GPA: 82.3\% (Rank: 16) \hfill 2006–2011
\end{itemize}

% Research
\section*{Research}
\textbf{Google Scholar Profile}: \href{https://scholar.google.com/citations?user=4ypH5kAAAAAJ&hl=en}{scholar.google.com} \\
\textbf{ORCID}: 0009-0001-2562-5694 \\
\textbf{Total Citations}: 72

\textbf{Peer-Reviewed Publications}
\begin{itemize}[left=0pt]
    \item Al-Khateeb, G., Al-Suleiman, T., Khedaywi, T., Elayan, M. (2016). “Studying Rutting Performance of Superpave Mixtures Using Unconfined Dynamic Creep and Simple Performance Tests.” \textit{Road Materials and Pavement Design}, Vol. 19 (2).
    \item Alsheyab, M., Khedaywi, T., Elayan, M. (2013). “Laboratory Study on Solidification/ Stabilization of Unwanted Medications Using Asphalt as a Binder.” \textit{Journal of Material Cycles and Waste Management}, Vol. 15 (2).
    \item Al-Suleiman, T., Elayan, M. (2013). “Gap Acceptance Behavior at U-turn Median Openings – Case Study in Jordan.” \textit{Jordan Journal of Civil Engineering}, Vol. 7 (3).
\end{itemize}

% Experience
\section*{Experience}
\textbf{University of Nebraska-Lincoln, Lincoln, NE, USA} \\
Graduate Research Assistant \hfill January 2023–Present \\
Graduate Teaching Assistant \hfill January 2024–Present \\
\begin{itemize}[left=0pt]
    \item Part of Dr. Jason Hawkins's research team at the Nebraska Transportation Center, focusing on transportation safety, planning, and advanced technologies for EVs and AVs.
    \item Teaching Assistant for Civil Engineering Analysis II and Principles of Transportation Engineering.
\end{itemize}
\newpage
\textbf{TrafQuest, Dubai, UAE} \\
Senior Transportation Engineer \hfill January 2019–January 2023 \\
Transportation Engineer \hfill June 2013–January 2019 \\
\begin{itemize}[left=0pt]
    \item Managed over 100 projects, including strategic transportation studies in the UAE and MENA region.
    \item Key tasks included travel demand forecasting, traffic analysis, roadway network performance evaluation, transport integration, and safety analysis.
\end{itemize}

\textbf{Jordan University of Science and Technology, Irbid, Jordan} \\
Research Assistant \hfill 2011 \\
Teaching Assistant \hfill 2012–2013 \\
\begin{itemize}[left=0pt]
    \item Conducted research on highway material performance and traffic operations optimization.
    \item Taught laboratory courses in Surveying, Highway Materials, and Engineering Statics.
\end{itemize}

% Core Capabilities
\section*{Core Capabilities}
\begin{itemize}[left=0pt]
    \item \textbf{Traffic analysis, Transport planning, Traffic management, Transport modeling}
    \item \textbf{Crash analysis, Geometric design, Statistical analysis, Research, Machine learning}
   \item \textbf{Software: Python, R, Julia, ArcGIS, QGIS, VISSIM, Synchro, SIDRA, SPSS}
\end{itemize}

\end{document}
